---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tvCoef

The goal of `tvCoef` is to study time-varying coefficients models around linear regression:

- piecewise regressions (using [`strucchange`](https://CRAN.R-project.org/package=strucchange) to detect the break dates) ;

- local regressions (using [`tvReg`](https://CRAN.R-project.org/package=tvReg)) ;

- state space models (using [`rjd3sts`](https://github.com/rjdverse/rjd3sts)).

## Installation

`tvCoef` relies on `rjd3sts` which need Java JRE  17 or later version.

To get the current stable version (from the latest release):

```{r, echo = TRUE, eval = FALSE}
# install.packages("remotes")
remotes::install_github("InseeFrLab/tvCoef@*release")
```

To get the current development version from GitHub:

```{r, echo = TRUE, eval = FALSE}
# install.packages("remotes")
remotes::install_github("InseeFrLab/tvCoef")
# or using r-universe:
install.packages('tvCoef', repos = c('https://aqlt.r-universe.dev', 'https://cloud.r-project.org'))
```

If you have troubles installing Java, check the [installation manual](https://github.com/jdemetra/rjdemetra/wiki/Installation-manual).

## Usage

```{r}
library(tvCoef)
data_gdp <- window(gdp, start = 1980, end = c(2019, 4))
reg_lin <- lm(
  formula = growth_gdp ~ bc_fr_m1 + diff_bc_fr_m1,
  data = data_gdp
)
reg_lin
ssm <- ssm_lm(
  reg_lin, 
  # To estimate the variance of the coefficient of the intercept            
  fixed_var_intercept = FALSE, var_intercept = 0.01,
  # To estimate the variance of the explanatory variable 
  fixed_var_variables = FALSE, var_variables = 0.01)
ssm
summary(ssm)
```


For more details on the methods, see the associated article available at <https://github.com/InseeFrLab/DT-tvcoef>.
